Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/concl.tex
done with pass

This paper presented the design and implementation of \textit{Nail},
an interface generator for data formats.  Nail helps programmers avoid
memory corruption and ambiguity vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
maintaining a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.

>>>>

This paper presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and ambiguity vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
maintaining a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this paper
are released as open-source software.

### 2014-05-02 paper/osdi14/eval.tex
done with pass

The results are shown in Figure~\ref{fig:perf-dns}, and demonstrate that
our Nail-based DNS server can achieve higher performance and lower latency
than BIND\@.  Although BIND is a much more sophisticated DNS server,
and implements many features that are not present in our Nail-based DNS
server, we believe our results demonstrate that Nail's parsers are not
a barrier to achieving acceptable performance.

>>>>

The results are shown in Figure~\ref{fig:perf-dns}, and demonstrate that
our Nail-based DNS server can achieve higher performance and lower latency
than BIND\@.  Although BIND is a more sophisticated DNS server,
and implements many features that are not present in our Nail-based DNS
server, we believe our results demonstrate that Nail's parsers are not
a barrier to achieving good performance.
